Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age

### 2020-10-29 README.Rmd
note on central illustration

>>>>

ASCVD = atherosclerotic cardiovascular disease; CKD = chronic kidney disease

_Note:_ This illustration is not the same as the central illustration in the paper. A different version is used in order to adhere to a publication agreement: "Excluding abstracts, none of the paper's contents have been previously published."

### 2020-10-29 doc/ACCAHA_BP_groups.Rmd
note on central illustration

_Note:_ This illustration is not the same as the central illustration in the paper. A different version is used in order to adhere to a publication agreement: "Excluding abstracts, none of the paper's contents have been previously published."

@@

ASCVD = atherosclerotic cardiovascular disease; CKD = chronic kidney disease

>>>>

@@

BP = blood presure; HTN = hypertension
